\bf Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-15 appendix.qmd
Updated the arrangement of equations

which given $s_1 < 0$ and $a_1 > 0$ will *always* be true. The same logic follows for @eq-equation4 and substituting $a_2 = \frac{\sqrt{3}}{2}a_1$, and $s_2 = -q \times r_2$ to @eq-equation4 can be written as,

@@

Also, substituting $a_2 = \frac{\sqrt{3}}{2}a_1$, $s_2 = -q \times r_2$ and rearranging @eq-equation5 gives:

@@

Therefore, if this equality is true, then $a_1 = \frac{(1+q)}{(b_1 - 1)}$, otherwise, $a_1 = \frac{2r_2(1+q)}{\sqrt{3}(b_2 - 1)}$.

>>>>

which given $s_1 < 0$ and $a_1 > 0$ will *always* be true. The same logic follows for @eq-equation4 and substituting $a_2 = \sqrt{3}a_1/{2}$, and $s_2 = -q \times r_2$ to @eq-equation4 can be written as,

@@

Also, substituting $a_2 = \sqrt{3}a_1/{2}$, $s_2 = -q \times r_2$ and rearranging @eq-equation5 gives:

@@

Therefore, if this equality is true, then 
$$
a_1 = \frac{(1+q)}{(b_1 - 1)},
$$
otherwise, 
$$
a_1 = \frac{2r_2(1+q)}{\sqrt{3}(b_2 - 1)}.
$$

### 2025-05-15 appendix.tex
Updated the arrangement
Updated the arrangement of equations

which given \(s_1 < 0\) and \(a_1 > 0\) will \emph{always} be true. The
same logic follows for Equation~\ref{eq-equation4} and substituting
\(a_2 = \frac{\sqrt{3}}{2}a_1\), and \(s_2 = -q \times r_2\) to
Equation~\ref{eq-equation4} can be written as,

@@

Also, substituting \(a_2 = \frac{\sqrt{3}}{2}a_1\),
\(s_2 = -q \times r_2\) and rearranging Equation~\ref{eq-equation5}
gives:

@@

Therefore, if this equality is true, then
\(a_1 = \frac{(1+q)}{(b_1 - 1)}\), otherwise,
\(a_1 = \frac{2r_2(1+q)}{\sqrt{3}(b_2 - 1)}\).

\newpage

@@

\begin{figure}

>>>>

which given \(s_1 < 0\) and \(a_1 > 0\) will \emph{always} be true. The
same logic follows for Equation~\ref{eq-equation4} and substituting
\(a_2 = \sqrt{3}a_1/{2}\), and \(s_2 = -q \times r_2\) to
Equation~\ref{eq-equation4} can be written as,

@@

Also, substituting \(a_2 = \sqrt{3}a_1/{2}\), \(s_2 = -q \times r_2\)
and rearranging Equation~\ref{eq-equation5} gives:

@@

Therefore, if this equality is true, then \[
a_1 = \frac{(1+q)}{(b_1 - 1)},
\] otherwise, \[
a_1 = \frac{2r_2(1+q)}{\sqrt{3}(b_2 - 1)}.
\]

@@
